---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lbl

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/lbl)](https://CRAN.R-project.org/package=lbl)
[![R-CMD-check](https://github.com/cole-brokamp/lbl/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cole-brokamp/lbl/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of lbl is to ...

## Installation

You can install the development version of lbl from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cole-brokamp/lbl")
```

## Overview

```{r}
library(lbl)
```

A labeled vector (`lbl_vec`) is a vector in R (see `?vctrs::vector_checks` for details) with a label attached. Convert a vector into a labeled vector with `as_lbl_vec` by passing a label character string.

```{r}
as_lbl_vec(letters, "The Alphabet")
```

Label is printed, but extract with `get_label()`

A labeled table (`lbl_tbl`) is

